---
title: "epi.branch.sim: First example"
author: "Henry Ngo"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{epi.branch.sim: First example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{css, echo=FALSE}
pre, code {white-space:pre !important; overflow-x:auto}
```

This vignette demonstrates how to run a single simple simulation example with `epi.branch.sim`. It assumes you have read [the introductory vignette](introduction.html) which gave a high level overview of the package, the simulation algorithm, and the description of the main simulation objects.

In this vignette, we will use the package's exposed functions to set up and run a simulation. We will examine the output and show how we can compute metrics from the output.

In other vignettes, we will look at how to use "driver" functions to set up a series of simulations, run them, and extract metrics to be used in analysis. This package also contains some example driver functions but more advanced analysis will require a user-customized driver function.

## Set up simulation
First, load the library and set a random seed for reproducibility.
```{r setup}
library(epi.branch.sim)
set.seed(3483)
```

Now we define parameters for the disease spread, interventions and other simulation control parameters. The following represent one example of these parameters and do not cover the entire range of options. For a detailed description of all options, please see the [Description of Parameters vignette](parameters.html).

### Define disease parameters
```{r setup disease params}
R0 <- 2.5
infect_dur <- 14  # in days
p_symp  <- 0.8 # percentage of cases that will be symptomatic
incub_params <- list(dist='lognormal',meanlog=1.57, sdlog=0.65) # distribution returns a value in days
generation_int_params <- list(dist='gamma', shape=2.29, rate=0.36)  # distribution returns a value in days
sec_infect_params <- list(type='Hellewell', disp=0.58) # 0.58 is the negative binomial dispersion parameter
```
The incubation period and generation interval distributions are from the incubation and serial interval distributions from [Bi et al. (2020)](https://www.medrxiv.org/content/10.1101/2020.03.03.20028423v3). These distribution parameters are passed as named lists that are interpreted by the package. For now, only pre-programmed distributions are available in this package. Run `?draw_incubation_period` and `?draw_generation_interval` to see what is currently available. The number of potential secondary infections are modelled in the same way as in [Hellewell et al. (2020)](https://doi.org/10.1016/S2214-109X(20)30074-7), i.e. drawn from a negative binomial distribution with mean equal to R0 and a dispersion parameter as provided in the `sec_infect_params` named list. Currently, this is the only way to model secondary infections, so no other value for `sec_infect_params$type` is accepted.

### Define intervention parameters
Tracing parameters:
```{r setup tracing params}
# Contact tracing parameters
do_variable_trace <- FALSE # use a constant tracing value (see next line)
p_trace <- 0.75 # all cases have a 75% chance of being traced
p_trace_app <- 0.75 # percentage of population using a contact tracing app
p_trace_app_comp <- 0.75 # percentage of population complying with contact tracing app isolation instructions
```

Timeline for isolation of cases:
```{r setup isolation}
# Set delays to isolation 
iso_delay_params <- list(
  dist='uniform', # the following are min/max ranges of a uniform distribution
  traced_min = 1, # traced secondary cases isolated 1-3 days after index case isolated
  traced_max = 3,
  untraced_min = 4, # untraced secondary cases isolated 4-5 days after *symptom onset*
  untraced_max = 5,
  untraced_pd_min = 2, # untraced secondary cases which are distancing isolated earlier
  untraced_pd_max = 3
)
```
Run `?draw_isolation_delay_period` or read the [parameters vignette](parameters.html) for more information on the above choices.

Physical (or social) distancing parameters:
```{r setup distancing}
pd_params <- list(
  pd_pop_frac = 0.8, # 80% of population are distancing
  pd_contact_rate1 = 1.0, # initial fraction of contacts for distancing group 
  pd_contact_rate2 = 0.3, # final fraction of contacts for distancing group 
  pd_change_t = 7 # simulation day number where the contact rate changes
)
```
Run `?draw_contact_rate` or read the [parameters vignette](parameters.html) for more information on the above choices. All contact rates are given with respect to the non-distancing group, which has a contact rate of 1.

### Define simulation control parameters (including imports)

Finally, a few important parameters that control how the simulation starts and runs. Setting up the introduction of imported cases is also done here.
```{r setup sim}
start_time <- 0 # start at time 0 (recommended)
dt <- 1 # timestep, in days
tmax <- 30 # total number of days in simulation
n_initial <- 3 # number of cases on day 0
import_params <- list(
  type = 'constant',
  rate = 1,  # one new import every day
  iso_lengths = 0, # number of days that imported cases might self-isolate upon arrival
  iso_p.group = 1  # probability that an imported case will do the above self-isolation
)
```
Run `?generate_imported_infections` or read the [parameters vignette](parameters.html) to see the other stochastic and deterministic options for the number of daily imported cases.

### Create initial simulation objects
This package has four functions to create and initialize the four simulation objects. We'll use the parameters we just defined to create these four objects

```{r create sim objects}
sim_params <- initialize_sim_params(
  R0, infect_dur, do_variable_trace, p_trace, 
  p_trace_app, p_trace_app_comp, p_symp, dt,
  incub_params, generation_int_params,
  iso_delay_params, sec_infect_params,
  import_params, pd_params)
sim_status <- initialize_sim_status(start_time,n_initial) 
state_df   <- create_state_df(n_initial,sim_params, sim_status, initialize=TRUE)
record_df  <- create_record_df(state_df, sim_status, initialize=TRUE)
```
Note that `sim_params` and `sim_status` need to be created first, because they are used as input to create the `state_df` and `record_df` objects.

Let’s take a look at the `sim_status` object:
```{r peek sim_status}
print(sim_status)
```
`sim_status` shows the current time (`t`) and the case ID of the most recent case generated (`last_case_id`). Here, we see that we are at time 0 and there has been 3 total cases at this time.


Let's now take a look at the first few rows of the `state_df` object to get a sense its structure and information content.
```{r peek state_df}
head(state_df)
```

Note that all initial cases are considered to be untraced. At the start of the simulation, the `contact_rate` for all cases is 1 because the distancing measures are delayed until day 7. Note that all times in `state_df` are measured in a relative sense: most times are measured from the start of infection, except for `isolation_delay`, which is measured from the symptom onset (`incubation_length`). The `generation_intervals` column stores the times where the case would cause a secondary infection. Here, we see that case 1 will cause an infection at time 0.73, i.e. by the next time-step. The column `non_infect_generations` lists potential secondary infections that were prevented due to that case's isolation. See `?create_state_df` or the [description of outputs vignette](outputs.html) for more information on these columns.

Now we can take a peek at `record_df`.
```{r peek record_df}
head(record_df)
```
This data frame stores information that was also available in the `state_df` data frame (e.g. `case_id`, `is_traced`, etc.) but provides additional columns for better tracking. While information is removed from `state_df` when it is no longer needed (for instance, the generation intervals list shortens as the infections are loaded into the simulation and rows are removed entirely when the case no longer has further pending infections), `record_df` retains all the information until the end of the simulation. Here, columns for milestones beginning with `d_` (e.g. `d_incub`) are durations measured as a relative time, in days. On the other hand, columns such as `t_symp` are absolute simulation times which have value `NA` until these milestones occur. Note that not all cases will reach all milestones. See `?create_record_df` or the [description of outputs vignette](outputs.html) for more information on how these columns are populated with information.


## Run simulation forward by one step
The function `step_simulation` is provided to advance the simulation by one time-step `dt` at a time. It takes the four simulation objects as input and returns the three objects that change over time (i.e. `sim_status', 'state_df' and 'record_df'). These outputs can be used as input for the next step forward. The following lines advance the simulation forward by one time-step and updates the simulation objects.

```{r run first step}
out <- step_simulation(sim_status, state_df, record_df, sim_params)
sim_status <- out$status
state_df <- out$state
record_df <- out$record
```

First, let's check that `sim_status` is updated.
```{r check sim_status}
print(sim_status)
```
This shows that we are now at time 1 (value of `t`) and there are 5 total cases (value of `last_case_id`). This is expected as our previous inspection of `state_df` tells us to expect one secondary infection from Case 1 within the first time-step and we have set up the simulation to add one imported case per day.

Let's now look at the `state_df` state vector.
```{r check state_df}
head(state_df)
```
We see that the first three cases now have their `days_infected` counter increased by 1. Cases 4 and 5 are new so their `days_infected` value is 0. We see that `n_sec_infects` for Case 1 has decreased from 9 to 8 and the first `generation_intervals` entry has been removed since that infection has already happened (Case 4). 

It's also worth noting how isolation removes potential infections. Looking at Case 4, we see that the isolation time is 7.01 days after initial infection (`incubation_length` of 2.26 days plus `isolation_delay` of 4.75 days). We also see that there will be 7 secondary infections from this case (`n_sec_infects=7`). The generation intervals for these 7 infections are listed in `generation_intervals` and the last one is 6.28 days. We can also see that there were 2 potential secondary infections that were prevented from happening: `non_infect_generations` shows prevented infections at 7.21 days and at 10.24 days past infection, for Case 4. The negative binomial draw for this case generated 9 potential infections and our intervention policies prevented 2 of them.

** Optional side note:** Case 4 is also the first manually traced case. The index case for Case 4 is Case 1, who would be isolated at 8 days (`incubation_length` of 3.3 days + `isolation_delay` of 4.7 days) past infection, or on simulation day 8 (since Case 1 was infected on day 0). Traced cases such as Case 4 are isolated at 1-3 days after their index case is isolated, so we would expect Case 4 to be isolated between day 9 and day 12. However, as discussed above, Case 4 will be isolated at 7.01 days past infection, so Case 4 is isolated around simulation day 8. This is because we also isolate untraced cases at 4-5 days past onset of symptoms (i.e. after `incubation_length`). If a case is isolated faster this way than through tracing, then the shorter delay is used. Here, because Case 1 had such a long isolation time, Case 4, while determined to be contact traced, is still isolated on the untraced case timeline. 

Let's now also look at the new `record_df`.
```{r check record_df}
head(record_df)
```
Much of the information here is the same as in the previous time-step. The `source` column is helpful to identify what caused the infection. We see that Case 4 was indeed caused by Case 1 and that Case 5 is an imported case. We also see that `n.sec_infects` in the `record_df` for Case 1 remains at 9 because `record_df` tracks the entire history or facts about each case while `state_df` just tracks what is necessary at a given time to advance the simulation. 

It's important to note that `t_inf` (and other `t_*` columns) are given at the discrete simulation time-steps only (i.e. multiples of `dt`, which is 1 in this example). Remember that the first generation interval of Case 1 was 0.73 days, which led to Case 4. For the purposes of propagating infections and calculating Case 4's isolation time, Case 4 was infected at time `t=0.73 days`. But in these columns, `t_inf` for Case 4 is on day 1. Thus, these columns indicate the time-step where the cases reach these milestones, not the actual time. These columns are best used for debugging rather than analysis.

## Run the simulation to final timestep
Now that we have run the simulation forward one time-step, we can just put everything in a loop and run it from the current step until `tmax` (in this example, `tmax=30`).

```{r finish sim}
for (t in (1+sim_status$t):tmax){ # t takes values 2,3,4,5,...30 (tmax)
  out <- step_simulation(sim_status, state_df, record_df, sim_params)
  sim_status <- out$status # update sim_status
  state_df <- out$state    # update state_df
  record_df <- out$record  # update record_df
}
```

Let's confirm that the simulation is where we expect and count the number of cases:
```{r check end of sim}
sim_status$t
nrow(state_df)
nrow(record_df)
```
The last recorded timestamp is 30 (days), corresponding to the value of `tmax` that we chose. There are 54 active cases at this point in time and 301 cases ever recorded by the simulation. Let's now look at the first few lines of `state_df`.

```{r check head state_df}
head(state_df, n=5)
```
These are the oldest active cases. The oldest entry here is Case 180, still in incubation after 11 days since this one has an incubation length of 31.5 days! 

Now let's look at the last few lines of `state_df`.
```{r check tail state_df}
tail(state_df, n=5)
```
These are the most recent five cases ending with Case #301. The negative value of `isolation_delay` in Case #300 indicates that this case will be isolated before the end of its incubation period. This happens because Case #300 is traced by the app which causes traced cases to be isolated as soon as the index case is isolated, leading to quick isolations. The value of 0.3 in the `contact_rate` column in three of the last five cases indicates that these cases are physically distancing and only have 0.3 times as many contacts as they normally would. 

We can also examine the first five lines of `record_df`.
```{r check head record_df}
head(record_df, n=5)
```
We see the first five cases again, however, now that the simulation is ended, these cases are resolved (i.e. either isolated or inactive in the `s_status` column). The time-steps when certain milestones are reached (e.g. `t_*` columns) are recorded with their values, while `NA` appears for milestones that didn't happen. For instance, Cases 2, 3, and 5 were asymptomatic, so no `t_symp` is recorded. The `cases_inf` column is meant to record the case IDs of the secondary infections but this bookkeeping item is not yet implemented. This information could be reconstructed from the `source` column.

## Retrieve metrics from simulation
While it could be interesting to examine the detailed case history of each simulation, typically, we want to do a statistical analysis to determine the distribution of various important quantities across many different simulations/realisations. We'll demonstrate some metrics that can be computed from `state_df` and `record_df`. 

### Counting number of cases of different statuses/types
A first example of a useful metric is obtained by simply counting the number of cases that are in various states at a given point in time. Note that these statements are in parentheses so that the result will be printed for the purposes of this vignette.
```{r echo=TRUE, count_cases}
(n.active <- nrow(state_df)) # all statuses except isolated or inactive
(n.total <- nrow(record_df)) # all cases, active or not
(n.incubation <- sum(record_df$s.status=='incubation')) # or any other status
(n.traced_by_app <- sum(record_df$is.traced_by_app))
(n.imported <- sum(record_df$source=='imported'))
```
Here, we have only generated one single simulation, but typically, we might have set up several hundred simulations with the same scenario parameters. We might loop over these simulations and in each iteration of the loop, these values would be stored in an output dataframe or vector that collects output from all the simulations. Also, here we are waiting until the final time-step before computing any metrics, but these metrics can also be captured at each time-step to create a time series per simulation. 

### New secondary and imported cases
In the above code chunks, we only used the first three named items in the output object `out` from `step_simulation()`. Let's see what else is available.
```{r examine_out}
names(out)
print(out$new_sec_cases)
print(out$new_imp_cases)
```
We see that there are two more outputs given at each time-step as a convienence. These are the number of new secondary cases generated at each step and the number of new imported cases added at each step. 

### Effective R or Rt
One other useful metric is the effective reproductive number $R_{\mathrm{eff}}$ or the instanteous reproductive number $R_t$. One way to compute $R_{\mathrm{eff}}$ is to consider the average number of secondary infections for each case:
```{r calc_Reff}
Reff <- mean(record_df$n.sec_infects)
print(Reff)
```
We see that over the course of the simulation, the tracing and distancing interventions have reduced the reproductive number from $R_0$ of 2.5 to an $R_{\mathrm{eff}}$ of 1.09.

Calculating $R_{\mathrm{eff}}$ in this way is a look back to the beginning of the simulation, but it may not be a good reflection of the current transmission rates. Instead, we might want to just look at infections that began in the past 7 days. We can do this by subsetting `record_df` to only include the cases generated in the past 7 days and repeating the calculation:
```{r calc_Rt7}
rec_df_last7 <- subset(record_df, t_inf > tmax-7) # record_df for infections from last 7 days
Rt <- mean(rec_df_last7$n.sec_infects)
print(Rt)
```
We see that for infections occurring during the last 7 days, the reproductive number is much lower, only 0.65, since we are not counting the earlier cases prior to distancing. 

## Simulation output
Typically, we will be running many simulations for one or more scenarios (set of parameters) through a "driver" function that sets up each scenario, loops through all the time-steps, computes metrics at each time-step and/or at the end of the simulation, and finally outputs something to be used in further analysis scripts. While the driver function can define the output in any way desired, typically a data frame or tibble is a good idea for storing this information. The columns could include some or all of the simulation parameters and the output metrics. Each row could be the value of each column at each time-step for each simulation (if time-series for each simulation is desired) or simply one summary value for each metric per simulation. An output arranged in this way is helpful because each simulation or scenario set of simulations can be run independently in parallel processes and saved to independent `.rds` files that are later combined with `rbindlist` or a similar function. 

### Outbreak determination
While many of the above presented metrics can be calculated at each time-step, some metrics are related to the end-state of a simulation. For example, we may want to know what fraction of simulations from a given scenario end in an outbreak. Because this is a stochastic branching process, when there are no imported cases, it is possible for the epidemic to "fizzle out". In [Hellewell et al. (2020)](https://doi.org/10.1016/S2214-109X(20)30074-7), they run the branching processes for three months and consider an outbreak controlled if there are no additional infections after this time. This determination is best done within the "driver" function at the final time-step and an example for the Hellewell implementation can be found in this package at `epi.branch.sim::run_scenario_Hellewell()`. Another method is to consider the $R_t$ value at the last time-step and consider simulations with $R_t$ greater than 1 as outbreaks. This can be done within the driver function as before, or in an analysis script.

## Next steps
In the future, we will present vignettes showing examples of this package applied to outbreak simulation on a large scale, such as a vignette reproducing the main results from [Hellewell et al. (2020)](https://doi.org/10.1016/S2214-109X(20)30074-7). We will also show vignettes that demonstrate one method to fit to reported case counts and forecast future case counts. They will be linked here when ready.

## References
[Bi et al. (2020)](https://www.medrxiv.org/content/10.1101/2020.03.03.20028423v3), "Epidemiology and Transmission of COVID-19 in Shenzhen China: Analysis of 391 cases and 1,286 of their close contacts", medRxiv 2020.03.03.20028423.

[Hellewell et al. (2020)](https://doi.org/10.1016/S2214-109X(20)30074-7), "Feasibility of controlling COVID-19 outbreaks by isolation of cases and contacts", *The Lancet Global Health*, Vol. 8, E488-E496.
